---
title: "Architectures results analysis"
author: "Katarzyna Sidorczuk"
date: "10/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 12)

library(dplyr)
library(ggplot2)
library(tidyr)
library(ggrepel)
library(targets)

tar_load(c(architectures_performance, mean_architecture_performance, model_variants))

arch_dat <- mutate(mean_architecture_performance,
                   arch_variant = sapply(mean_architecture_performance[["model"]], function(i) gsub("-Sec|-Tat", "", strsplit(i, "_")[[1]][2])),
                   hierarchical = grepl(pattern = "Filtering", x = model, ignore.case = FALSE),
                   sec = !grepl(pattern = "-Sec", x = model, ignore.case = FALSE),
                   tat = !grepl(pattern = "-Tat", x = model, ignore.case = FALSE),
                   smote = !grepl(pattern = "0-1", x = model),
                   smote_variant = sapply(mean_architecture_performance[["model"]], function(i) strsplit(i, "_")[[1]][3])) %>% 
  pivot_longer(cols = !c(model, arch_variant, hierarchical, sec, tat, smote, smote_variant), names_to = "measure") 

```

## Architecture variants

```{r}
data.frame(arch_variant = names(model_variants)[1:8], 
           models = sapply(model_variants[1:8], function(i) paste0(i, collapse = ", "))) %>% 
  knitr::kable(., row.names = FALSE)
```

## Overall performance with hierarchical or not hierarchical architecture

```{r fig.height=6}
filter(arch_dat, measure %in% c("mean_AU1U", "mean_kappa")) %>% 
  ggplot(aes(x = arch_variant, y = value, color = hierarchical)) +
  geom_boxplot() +
  facet_wrap(~measure, scales = "free_y", nrow = 2) + 
  theme_bw()
```

## Prediction of all classes with hierarchical or not hierarchical architecture

```{r fig.height=15}
filter(arch_dat, !(measure %in% c("mean_AU1U", "mean_kappa"))) %>% 
  ggplot(aes(x = arch_variant, y = value, color = measure)) +
  geom_boxplot() +
  facet_grid(measure~hierarchical, scales = "free_y") + 
  theme_bw() +
  theme(legend.position = "none")
```

## Prediction of the most difficult classes with hierarchical or not hierarchical architecture
```{r fig.height=6}
filter(arch_dat, measure %in% c("mean_N_IM_sensitivity", "mean_N_OM_sensitivity", "mean_N_TM_sensitivity", "mean_N_TL_SEC_sensitivity")) %>% 
  ggplot(aes(x = arch_variant, y = value, color = measure)) +
  geom_boxplot() +
  facet_wrap(~hierarchical) + 
  theme_bw() +
  theme(legend.position = "bottom")
```

## Prediction of the most difficult classes depending on the number of models that use SMOTE

```{r fig.height=14}
filter(arch_dat, measure %in% c("mean_N_IM_sensitivity", "mean_N_OM_sensitivity", "mean_N_TM_sensitivity", "mean_N_TL_SEC_sensitivity")) %>% 
  mutate(n_smote_models = sapply(strsplit(smote_variant, "-"), function(i) i[1])) %>% 
  ggplot(aes(x = n_smote_models, y = value, color = hierarchical)) +
  geom_boxplot() +
  facet_grid(measure~arch_variant, scales = "free") +
  theme_bw() +
  theme(legend.position = "bottom")
```

## Overall performance depending on presence of Sec and Tat models in the architecture

```{r fig.height=6}
filter(arch_dat, measure %in% c("mean_AU1U", "mean_kappa")) %>% 
  mutate(models = case_when(sec == TRUE & tat == TRUE ~ "with Sec and Tat",
                            sec == FALSE & tat == TRUE ~ "without Sec",
                            sec == TRUE & tat == FALSE ~ "without Tat")) %>% 
  ggplot(aes(x = models, y = value, color = measure)) +
  geom_boxplot() +
  facet_grid(measure~arch_variant, scales = "free_y") + 
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))
```

## Performance on HMM-dependent classes depending on presence of Sec and Tat models in the architecture

```{r fig.height=11}
filter(arch_dat, measure %in% c("mean_N_TL_SEC_sensitivity", "mean_N_TL_TAT_sensitivity", "mean_N_S_sensitivity")) %>% 
  mutate(models = case_when(sec == TRUE & tat == TRUE ~ "with Sec and Tat",
                            sec == FALSE & tat == TRUE ~ "without Sec",
                            sec == TRUE & tat == FALSE ~ "without Tat")) %>% 
  ggplot(aes(x = models, y = value, color = measure)) +
  geom_boxplot() +
  facet_grid(measure~arch_variant, scales = "free_y") + 
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90))
```

## Performance on HMM models-dependent classes depending on presence of Sec and Tat models and hierarchy in the architecture

```{r fig.height=11}
filter(arch_dat, measure %in% c("mean_N_TL_SEC_sensitivity", "mean_N_TL_TAT_sensitivity", "mean_N_S_sensitivity")) %>% 
  mutate(models = case_when(sec == TRUE & tat == TRUE ~ "with Sec and Tat",
                            sec == FALSE & tat == TRUE ~ "without Sec",
                            sec == TRUE & tat == FALSE ~ "without Tat")) %>% 
  ggplot(aes(x = models, y = value, color = hierarchical)) +
  geom_boxplot() +
  facet_grid(measure~arch_variant, scales = "free_y") + 
  theme_bw()+
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90))
```


## Performance of all architectures based on variant 8

Mean Kappa and AU1U
```{r fig.height=12}
plot_dat <- filter(arch_dat, arch_variant == "v8", hierarchical == FALSE) %>% 
  pivot_wider(names_from = "measure", values_from = "value") %>% 
  mutate(models = case_when(sec == TRUE & tat == TRUE ~ "with Sec and Tat",
                            sec == FALSE & tat == TRUE ~ "without Sec",
                            sec == TRUE & tat == FALSE ~ "without Tat"),
         type = gsub("_Filtering_0.5", "", gsub("Architecture_v8_|Architecture_v8-Sec_|Architecture_v8-Tat_", "", model)))

ggplot(plot_dat, aes(x = mean_kappa, y = mean_AU1U, color = type)) +
  geom_point(aes(shape = models), size = 2) +
  geom_text_repel(label = plot_dat[["model"]]) +
  theme_bw() +
  coord_equal()
```

Mean N_IM and N_OM sensitivity
```{r fig.height=12}
ggplot(plot_dat, aes(x = mean_kappa, y = mean_N_IM_sensitivity, z = mean_N_OM_sensitivity, color = type)) +
  geom_point(aes(shape = models), size = 2) +
  geom_text_repel(label = plot_dat[["model"]], size = 3, max.overlaps = 15) +
  theme_bw() 

```

Performance of architectures based on variant 8 (excluding architectures without Tat models as their overall performance is significantly lower) in 10-fold CV
```{r fig.height=12}
filter(architectures_performance, grepl("v8_|v8-Sec", model) & grepl("No_filtering", model)) %>% 
  pivot_longer(cols = !c(model, fold)) %>% 
  ggplot(aes(y = model, x = value)) +
  geom_boxplot() +
  facet_wrap(~name, scales = "free_x") +
  theme_bw()
```

Performance of the five best architectures (according to mean kappa value) in 10-fold CV
```{r fig.height=12}
filter(architectures_performance, model %in% c("Architecture_v8-Sec_2-1_No_filtering", "Architecture_v8_1-2_No_filtering", "Architecture_v8_2-1_No_filtering", 
                       "Architecture_v8-Sec_1-2_No_filtering", "Architecture_v8_2-3_No_filtering"))  %>% 
  mutate(model = factor(model, levels = rev(c("Architecture_v8-Sec_2-1_No_filtering", "Architecture_v8_1-2_No_filtering", "Architecture_v8_2-1_No_filtering", 
                                          "Architecture_v8-Sec_1-2_No_filtering", "Architecture_v8_2-3_No_filtering")))) %>% 
  pivot_longer(cols = !c(model, fold)) %>% 
  ggplot(aes(y = model, x = value)) +
  geom_boxplot() +
  facet_wrap(~name, scales = "free_x") +
  theme_bw()
```
