---
title: "Dataset exploration"
author: "Katarzyna Sidorczuk"
date: "11/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 12, fig.height = 9)

library(ggplot2)
library(tidyr)
library(ggrepel)
library(targets)
library(ggbiplot)
library(dplyr)
library(biogram)
library(factoextra)
source("functions/ngram_model_functions.R")

tar_load(c(N_TL_SEC_seqs, N_TL_TAT_seqs, N_S_seqs, N_OM_seqs, N_IM_seqs, N_TM_seqs,
           P_S_seqs, P_IM_seqs, P_TM_seqs, ngram_matrix, data_df_final, PlastoGram_ngram_models))

seqs <- list("N_TL_SEC" = N_TL_SEC_seqs, "N_TL_TAT" = N_TL_TAT_seqs, "N_S" = N_S_seqs, "N_OM" = N_OM_seqs, 
             "N_IM" = N_IM_seqs, "N_TM" = N_TM_seqs, "P_S" = P_S_seqs, "P_IM" = P_IM_seqs, "P_TM" = P_TM_seqs)

aa_comp <- lapply(names(seqs), function(ith_set) {
  aa <- as.matrix(table(unlist(unname(seqs[[ith_set]]))))/length(unlist(seqs[[ith_set]])) 
  data.frame(aa = row.names(aa),
             freq = aa[,1],
             dataset = ith_set)
}) %>% bind_rows()

aa_comp_peptides <- lapply(names(seqs), function(i) {
  ds <- seqs[[i]]
  lapply(names(ds), function(ith_prot) {
    data.frame(table(factor(ds[[ith_prot]], levels = c("A", "C", "D", "E", "F", "G", "H",
                                                       "I", "K", "L", "M", "N", "P", "Q",
                                                       "R", "S", "T", "V", "W", "Y")))/length(ds[[ith_prot]])) %>%
      setNames(c("Amino acid", "Frequency"))  %>%
      mutate(dataset = i,
             prot_name = ith_prot)
  }) %>% bind_rows()
}) %>% bind_rows() %>% 
  mutate(dataset = ifelse(dataset %in% c("N_TL_TAT", "N_TL_SEC"), "N_TL", dataset)) %>% 
  pivot_wider(names_from = "Amino acid", values_from = "Frequency") %>% 
  mutate(Source = ifelse(grepl("P_", dataset), "Plastid", "Nuclear"),
         Stroma = ifelse(grepl("_S$", dataset), TRUE, FALSE),
         type = case_when(
           dataset %in% c("N_TM", "P_TM") ~ "TM",
           dataset %in% c("N_IM", "P_IM") ~ "IM",
           dataset %in% c("N_S", "P_S") ~ "Stroma",
           dataset == "N_OM" ~ "OM",
           dataset == "N_TL" ~ "TL"
         )) 

ngram_data <- mutate(data_df_final) %>% 
  mutate(dataset = ifelse(dataset %in% c("N_TL_TAT", "N_TL_SEC"), "N_TL", dataset)) %>% 
  mutate(Source = ifelse(grepl("P_", dataset), "Plastid", "Nuclear"),
         Stroma = ifelse(grepl("_S$", dataset), TRUE, FALSE),
         type = case_when(
           dataset %in% c("N_TM", "P_TM") ~ "TM",
           dataset %in% c("N_IM", "P_IM") ~ "IM",
           dataset %in% c("N_S", "P_S") ~ "Stroma",
           dataset == "N_OM" ~ "OM",
           dataset == "N_TL" ~ "TL"
         )) 

seqs_colors_all <- c("N_OM" = "#8210c9", "N_IM" = "#344feb", "P_IM" = "#69cdff", "N_TL_SEC" = "#ccbf10", "N_TL_TAT" = "#fff575", 
                     "N_TM" = "#911a1a", "P_TM" = "#ff7d7d", "N_S" = "#118a0c", "P_S" = "#9fff9c")

seqs_colors <- c("N_OM" = "#8210c9", "N_IM" = "#344feb", "P_IM" = "#69cdff", "N_S" = "#118a0c", "P_S" = "#9fff9c", 
                 "N_TM" = "#911a1a", "P_TM" = "#ff7d7d", "N_TL" = "#ccbf10")

colors <- c("#8210c9", "#344feb", "#69cdff", "#ccbf10", "#fff575", "#911a1a", "#ff7d7d", "#118a0c", "#9fff9c")
```


## Amino acid composition

### Composition of whole datasets 
```{r fig.height=10}
ggplot(aa_comp, aes(x = dataset, y = freq, fill = dataset, group = dataset, color = dataset)) +
  geom_col(position = "dodge", alpha = 0.5) +
  facet_wrap(~aa, scales = "free_x") +
  scale_fill_manual(values = seqs_colors_all) +
  scale_color_manual(values = seqs_colors_all) +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90)) 
```

### PCA on amino acid composition of peptides
```{r}
pca_res <- prcomp(select(aa_comp_peptides, -c("dataset", "prot_name", "Source", "Stroma", "type")), center = TRUE)
plot_dat <- mutate(aa_comp_peptides, 
                   PC1 = pca_res[["x"]][, "PC1"],
                   PC2 = pca_res[["x"]][, "PC2"]) 

ggbiplot(pca_res, groups = aa_comp_peptides[["dataset"]], ellipse = TRUE, alpha = 0.5) +
  theme_bw() +
  scale_color_manual("Dataset", values = seqs_colors) 

plot_dat %>% 
  ggplot(aes(x = PC1, y = PC2, fill = dataset, color = dataset)) +
  geom_point(alpha = 0.25, size = 1) +
  stat_density_2d(aes(alpha = ..level..), geom = "polygon", color = "black", size = 0.2) +
  scale_color_manual(values = seqs_colors) +
  scale_fill_manual(values = seqs_colors) +
  facet_wrap(~dataset) +
  theme_bw() +
  theme(legend.position = "none")

plot_dat %>% 
  ggplot(aes(x = PC1, y = PC2, fill = dataset, color = dataset)) +
  geom_point(alpha = 0.5, size = 1) +
  scale_color_manual(values = seqs_colors) +
  scale_fill_manual(values = seqs_colors) +
  facet_wrap(~dataset) +
  theme_bw() +
  theme(legend.position = "none")

plot_dat %>% 
  filter(dataset %in% c("N_IM", "N_S", "P_S")) %>% 
  ggplot(aes(x = PC1, y = PC2, fill = dataset, color = dataset)) +
  stat_density_2d(aes(alpha = ..level..), geom = "polygon", color = "black", size = 0.2) +
  scale_color_manual(values = seqs_colors[c("N_S", "P_S", "N_IM")]) +
  scale_fill_manual(values = seqs_colors[c("N_S", "P_S", "N_IM")]) +
  theme_bw()
```
```{r fig.height=5}
plot_dat %>% 
  ggplot(aes(x = PC1, y = PC2, fill = dataset, color = dataset)) +
  stat_density_2d(aes(alpha = ..level..), geom = "polygon", color = "black", size = 0.2) +
  scale_color_manual(values = seqs_colors) +
  scale_fill_manual(values = seqs_colors) +
  facet_wrap(~Source) +
  theme_bw()
```
```{r}
plot_dat %>% 
  ggplot(aes(x = PC1, y = PC2, fill = dataset, color = dataset)) +
  stat_density_2d(aes(alpha = ..level..), geom = "polygon", color = "black", size = 0.2) +
  scale_color_manual(values = seqs_colors) +
  scale_fill_manual(values = seqs_colors) +
  facet_grid(Stroma~Source) +
  theme_bw()

```


## n-gram composition

### PCA on n-gram composition of peptides (all n-grams)
```{r}
pca_ngram_res <- prcomp(ngram_matrix, center = TRUE)
plot_dat_ngrams <- mutate(ngram_data, 
                          PC1 = pca_ngram_res[["x"]][, "PC1"],
                          PC2 = pca_ngram_res[["x"]][, "PC2"]) 

ggbiplot(pca_ngram_res, groups = plot_dat_ngrams[["dataset"]], ellipse = TRUE, alpha = 0.5, var.axes = FALSE) +
  theme_bw() +
  scale_color_manual("Dataset", values = seqs_colors) 

plot_dat_ngrams %>% 
  ggplot(aes(x = PC1, y = PC2, fill = dataset, color = dataset)) +
  geom_point(alpha = 0.5, size = 1) +
  scale_color_manual(values = seqs_colors) +
  scale_fill_manual(values = seqs_colors) +
  facet_wrap(~dataset) +
  theme_bw() +
  theme(legend.position = "none")
```

### PCA on n-gram composition of peptides using Stroma_model informative n-grams 

```{r}
stroma_model_imp_ngrams <- calc_imp_ngrams(ngram_matrix, target = ngram_data[["Stroma"]], cutoff = 0.01)
print("Number of informative n-grams: ", length(stroma_model_imp_ngrams))

pca_ngram_res2 <- prcomp(ngram_matrix[, stroma_model_imp_ngrams], center = TRUE)
plot_dat_ngrams <- mutate(ngram_data, 
                          PC1 = pca_ngram_res2[["x"]][, "PC1"],
                          PC2 = pca_ngram_res2[["x"]][, "PC2"]) 

ggbiplot(pca_ngram_res2, groups = plot_dat_ngrams[["dataset"]], ellipse = TRUE, alpha = 0.5, var.axes = FALSE) +
  theme_bw() +
  scale_color_manual("Dataset", values = seqs_colors) 

plot_dat_ngrams %>% 
  ggplot(aes(x = PC1, y = PC2, color = Stroma)) +
  geom_point(alpha = 0.5, size = 1) +
  scale_color_manual(values = c(`TRUE` = "#118a0c", `FALSE` = "#8210c9")) +
  theme_bw()

plot_dat_ngrams %>% 
  ggplot(aes(x = PC1, y = PC2, fill = Stroma, color = Stroma)) +
  geom_point(alpha = 0.5, size = 1) +
  stat_density_2d(aes(alpha = ..level..), geom = "polygon", color = "black", size = 0.2) +
  scale_color_manual(values = c(`TRUE` = "#118a0c", `FALSE` = "#8210c9")) +
  scale_fill_manual(values = c(`TRUE` = "#118a0c", `FALSE` = "#8210c9")) +
  theme_bw()
```
```{r fig.height = 5}
plot_dat_ngrams %>% 
  ggplot(aes(x = PC1, y = PC2, fill = Stroma, color = Stroma)) +
  geom_point(alpha = 0.5, size = 1) +
  stat_density_2d(aes(alpha = ..level..), geom = "polygon", color = "black", size = 0.2) +
  scale_color_manual(values = c(`TRUE` = "#118a0c", `FALSE` = "#8210c9")) +
  scale_fill_manual(values = c(`TRUE` = "#118a0c", `FALSE` = "#8210c9")) +
  theme_bw() +
  facet_wrap(~Stroma)
```
40 n-grams with the highest contribution to the PC1 and PC2 (20 best for each component)
```{r}
res_var <- get_pca_var(pca_ngram_res2)

pc1_vars <- res_var[["contrib"]][,1:2] %>% 
    as.data.frame() %>% 
    add_rownames() %>% 
    arrange(desc(`Dim.1`)) %>% 
    head(n = 20) %>% 
    .[["rowname"]]

pc2_vars <- res_var[["contrib"]][,1:2] %>% 
    as.data.frame() %>% 
    add_rownames() %>% 
    arrange(desc(`Dim.2`)) %>% 
    head(n = 20) %>% 
    .[["rowname"]]

fviz_pca_var(pca_ngram_res2,
             col.var = "contrib", 
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE, select.var = list(name = c(pc1_vars, pc2_vars))
)

```

### PCA on n-gram composition of peptides using P_stroma_model informative n-grams 
```{r}
p_stroma_model_imp_ngrams <- calc_imp_ngrams(ngram_matrix[which(data_df_final[["Nuclear_target"]] == FALSE), ], 
                                             target = filter(ngram_data, Source == "Plastid")[["Stroma"]], 
                                             cutoff = 0.01)
print("Number of informative n-grams: ", length(p_stroma_model_imp_ngrams))

pca_ngram_res3 <- prcomp(ngram_matrix[, p_stroma_model_imp_ngrams], center = TRUE)
plot_dat_ngrams <- mutate(ngram_data, 
                          PC1 = pca_ngram_res3[["x"]][, "PC1"],
                          PC2 = pca_ngram_res3[["x"]][, "PC2"]) 

ggbiplot(pca_ngram_res3, groups = plot_dat_ngrams[["dataset"]], ellipse = TRUE, alpha = 0.5, var.axes = FALSE) +
  theme_bw() +
  scale_color_manual("Dataset", values = seqs_colors) 

plot_dat_ngrams %>% 
  ggplot(aes(x = PC1, y = PC2, color = Stroma)) +
  geom_point(alpha = 0.5, size = 1) +
  scale_color_manual(values = c(`TRUE` = "#118a0c", `FALSE` = "#8210c9")) +
  theme_bw() +
  facet_wrap(~Source)

plot_dat_ngrams %>% 
  ggplot(aes(x = PC1, y = PC2, fill = Stroma, color = Stroma)) +
  geom_point(alpha = 0.5, size = 1) +
  stat_density_2d(aes(alpha = ..level..), geom = "polygon", color = "black", size = 0.2) +
  scale_color_manual(values = c(`TRUE` = "#118a0c", `FALSE` = "#8210c9")) +
  scale_fill_manual(values = c(`TRUE` = "#118a0c", `FALSE` = "#8210c9")) +
  theme_bw() +
  facet_wrap(~Source)
```
40 n-grams with the highest contribution to the PC1 and PC2 (20 best for each component)
```{r}
res_var <- get_pca_var(pca_ngram_res3)

pc1_vars <- res_var[["contrib"]][,1:2] %>% 
    as.data.frame() %>% 
    add_rownames() %>% 
    arrange(desc(`Dim.1`)) %>% 
    head(n = 20) %>% 
    .[["rowname"]]

pc2_vars <- res_var[["contrib"]][,1:2] %>% 
    as.data.frame() %>% 
    add_rownames() %>% 
    arrange(desc(`Dim.2`)) %>% 
    head(n = 20) %>% 
    .[["rowname"]]

fviz_pca_var(pca_ngram_res3,
             col.var = "contrib", 
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE, select.var = list(name = c(pc1_vars, pc2_vars))
)
```


### PCA on n-gram composition of peptides using N_stroma_model informative n-grams 
```{r}
n_stroma_model_imp_ngrams <- calc_imp_ngrams(ngram_matrix[which(data_df_final[["Nuclear_target"]] == TRUE), ], 
                                             target = filter(ngram_data, Source == "Nuclear")[["Stroma"]], 
                                             cutoff = 0.01)
print("Number of informative n-grams: ", length(n_stroma_model_imp_ngrams))

pca_ngram_res4 <- prcomp(ngram_matrix[, n_stroma_model_imp_ngrams], center = TRUE)
plot_dat_ngrams <- mutate(ngram_data, 
                          PC1 = pca_ngram_res4[["x"]][, "PC1"],
                          PC2 = pca_ngram_res4[["x"]][, "PC2"]) 

ggbiplot(pca_ngram_res4, groups = plot_dat_ngrams[["dataset"]], ellipse = TRUE, alpha = 0.5, var.axes = FALSE) +
  theme_bw() +
  scale_color_manual("Dataset", values = seqs_colors) 

plot_dat_ngrams %>% 
  ggplot(aes(x = PC1, y = PC2, color = Stroma)) +
  geom_point(alpha = 0.5, size = 1) +
  scale_color_manual(values = c(`TRUE` = "#118a0c", `FALSE` = "#8210c9")) +
  theme_bw() +
  facet_wrap(~Source)

plot_dat_ngrams %>% 
  ggplot(aes(x = PC1, y = PC2, fill = Stroma, color = Stroma)) +
  geom_point(alpha = 0.5, size = 1) +
  stat_density_2d(aes(alpha = ..level..), geom = "polygon", color = "black", size = 0.2) +
  scale_color_manual(values = c(`TRUE` = "#118a0c", `FALSE` = "#8210c9")) +
  scale_fill_manual(values = c(`TRUE` = "#118a0c", `FALSE` = "#8210c9")) +
  theme_bw() +
  facet_wrap(~Source)
```
40 n-grams with the highest contribution to the PC1 and PC2 (20 best for each component)
```{r}
res_var <- get_pca_var(pca_ngram_res4)

pc1_vars <- res_var[["contrib"]][,1:2] %>% 
    as.data.frame() %>% 
    add_rownames() %>% 
    arrange(desc(`Dim.1`)) %>% 
    head(n = 20) %>% 
    .[["rowname"]]

pc2_vars <- res_var[["contrib"]][,1:2] %>% 
    as.data.frame() %>% 
    add_rownames() %>% 
    arrange(desc(`Dim.2`)) %>% 
    head(n = 20) %>% 
    .[["rowname"]]

fviz_pca_var(pca_ngram_res4,
             col.var = "contrib", 
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE, select.var = list(name = c(pc1_vars, pc2_vars))
)
```

