---
title: "FCBF_QuipT_comparison"
author: "Katarzyna Sidorczuk"
date: "9/6/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)
library(targets)
library(dplyr)

tar_load(list.files("./_targets/objects"))

```

## Plastid_Nuclear model

QuiPT cut-off = 0.001
```{r}
kable(Plastid_Nuclear_CV_res_stats)
```
FCBF
```{r}
kable(Plastid_Nuclear_FCBF_CV_res)
```

## Membrane_Notmembrane model
QuiPT cut-off = 0.001
```{r}
kable(Membrane_Notmembrane_CV_res_stats)
```
FCBF
```{r}
kable(Membrane_Notmembrane_FCBF_CV_res)
```

## Nuclear_Membrane model
QuiPT cut-off = 0.001
```{r}
kable(Membrane_Nuclear_CV_res_stats)
```
QuiPT cut-off = 0.01
```{r}
kable(Membrane_Nuclear_CV_2_res_stats)
```
FCBF
```{r}
kable(Nuclear_Membrane_FCBF_CV_res)
```

## Plastid_Membrane model
QuiPT cut-off = 0.001
```{r}
kable(Membrane_Plastid_CV_res_stats)
```
FCBF
```{r}
kable(Plastid_Membrane_FCBF_CV_res)
```

## Stroma model
QuiPT cut-off = 0.001
```{r}
kable(Stroma_CV_res_stats)
```
FCBF
```{r}
kable(Stroma_FCBF_CV_res)
```

## Nuclear_Stroma model
QuiPT cut-off = 0.001
```{r}
kable(N_stroma_CV_res_stats)
```
FCBF
```{r}
kable(N_Stroma_FCBF_CV_res)
```

## Plastid_Stroma model
QuiPT cut-off = 0.001
```{r}
kable(P_stroma_CV_res_stats)
```
FCBF
```{r}
kable(P_Stroma_FCBF_CV_res)
```


## OM_Stroma model
QuiPT cut-off = 0.001
```{r}
kable(OM_Stroma_CV_res_stats)
```
QuiPT cut-off = 0.01
```{r}
kable(OM_Stroma_CV_2_res_stats)
```
FCBF
```{r}
kable(OM_Stroma_FCBF_CV_res)
```

## Nuclear OM vs. other membrane model
QuiPT cut-off = 0.001
```{r}
kable(OM_other_membrane_CV_res_stats)
```
FCBF
```{r}
kable(OM_other_membrane_FCBF_CV_res)
```

## Nuclear IM vs. other membrane model
QuiPT cut-off = 0.001
```{r}
kable(IM_other_membrane_CV_res_stats)
```
FCBF
```{r}
kable(IM_other_membrane_FCBF_CV_res)
```

## Nuclear TM vs. other membrane model
QuiPT cut-off = 0.001
```{r}
kable(TM_other_membrane_CV_res_stats)
```
FCBF
```{r}
kable(TM_other_membrane_FCBF_CV_res)
```

