---
title: "Graph-part results"
author: "Katarzyna Sidorczuk"
date: "3/4/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, fig.height = 10, fig.width = 12)

library(dplyr)
library(ggplot2)
library(tidyr)
library(DT)

data_path <- "~/Dropbox/Projekty/BioNgramProjects/PlastoGram/"
datasets <- c("N_OM", "N_IM", "P_IM", "N_S", "P_S", "N_TM", "P_TM", "N_TL_SEC", "N_TL_TAT")

options(DT.options = list(dom = "Brtip",
                          buttons = c("copy", "csv", "excel", "print"),
                          pageLength = 20
))

my_DT <- function(x, ...)
  datatable(x, ..., escape = FALSE, extensions = 'Buttons', filter = "top", rownames = FALSE,
            style = "bootstrap")

plot_graphpart_res <- function(res_file) {
  x <- read.csv(res_file)
  y <- x %>% group_by(`label.val`, cluster) %>% summarise(n = n()) 
  nam <- data.frame(`label.val` = 0:8, 
                    dataset = datasets)
  
  all_res <- left_join(y, nam)
  
  all_res %>% 
    mutate(cluster = as.factor(cluster)) %>% 
    ggplot(aes(x = cluster, y = n)) +
    geom_col() +
    geom_text(aes(label = n), vjust = -0.5, size = 3) +
    facet_wrap(~dataset, scales = "free_y")
}

combine_and_plot_graphpart_res <- function(type, datasets) {
  all_dat <- lapply(datasets, function(ith_set) {
    tryCatch({
      read.csv(paste0(data_path, "Graph-part_results/graphpart_res_", ith_set, "_", type, ".csv")) %>% 
        mutate(dataset = ith_set) 
    }, error = function(e) data.frame())
  }) %>% bind_rows()
  
  all_res <- all_dat %>% 
    group_by(dataset, cluster) %>% 
    summarise(n = n()) 
  
  all_res %>% 
    mutate(cluster = as.factor(cluster)) %>% 
    ggplot(aes(x = cluster, y = n)) +
    geom_col() +
    geom_text(aes(label = n), vjust = -0.5, size = 3) +
    facet_wrap(~dataset, scales = "free_y")
}

nam <- data.frame(`label.val` = 0:8, 
                    dataset = datasets)
```

## Summary

```{r}
all_res_files <- list.files(paste0(data_path, "Graph-part_results/"), full.names = TRUE, pattern = ".csv")
whole_dataset_res_files <- all_res_files[!(grepl("N|P", all_res_files))]
all_res <- lapply(whole_dataset_res_files, function(ith_file) {
  read.csv(ith_file) %>% 
    mutate(file = gsub(".csv", "", last(strsplit(ith_file, "/")[[1]]))) %>% 
    left_join(nam) %>% 
    group_by(file, dataset, cluster) %>% 
    summarise(n = n()) %>% 
    ungroup() %>% 
    pivot_wider(names_from = cluster, values_from = n, values_fill = 0) %>% 
    pivot_longer(3:ncol(.), names_to = "cluster", values_to = "n")
}) %>% bind_rows()

stats <- all_res %>% 
  group_by(file, dataset) %>% 
  summarise(sum_n = sum(n),
            mean = mean(n),
            sd = sd(n),
            `sd/sum_n` = sd/sum_n) %>% 
  arrange(`sd/sum_n`)

my_DT(stats)
```

Sum of sd/sum_n for all classes
```{r}
stats %>% 
  summarise(sd_sum = sum(`sd/sum_n`)) %>% 
  arrange(sd_sum) %>% 
  my_DT()
```

## CD-HIT reduction 99%

30%, 4 clusters
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.99.fa --threshold 0.3 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.99_4.csv --labels-name label --partitions 4 --threads 24 --save-checkpoint-path graph-part_edgelist_99.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.99_4.csv"))
```

30%, 5 clusters
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.99.fa --threshold 0.3 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.99_5.csv --labels-name label --partitions 5 --edge-file graph-part_edgelist_99.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.99_5.csv"))
```

30%, 6 clusters
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.99.fa --threshold 0.3 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.99_6.csv --labels-name label --partitions 6 --edge-file graph-part_edgelist_99.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.99_6.csv"))
```

40%, 4 clusters
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.99.fa --threshold 0.4 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.99_4_thresh0.4.csv --labels-name label --partitions 4 --edge-file graph-part_edgelist_99.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.99_4_thresh0.4.csv"))
```

40%, 5 clusters
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.99.fa --threshold 0.4 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.99_5_thresh0.4.csv --labels-name label --partitions 5 --edge-file graph-part_edgelist_99.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.99_5_thresh0.4.csv"))
```

40%, 6 clusters
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.99.fa --threshold 0.4 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.99_6_thresh0.4.csv --labels-name label --partitions 6 --edge-file graph-part_edgelist_99.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.99_6_thresh0.4.csv"))
```

50%, 4 clusters
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.99.fa --threshold 0.5 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.99_4_thresh0.5.csv --labels-name label --partitions 4 --edge-file graph-part_edgelist_99.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.99_4_thresh0.5.csv"))
```

50%, 5 clusters
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.99.fa --threshold 0.5 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.99_5_thresh0.5.csv --labels-name label --partitions 5 --edge-file graph-part_edgelist_99.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.99_5_thresh0.5.csv"))
```

50%, 6 clusters
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.99.fa --threshold 0.5 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.99_6_thresh0.5.csv --labels-name label --partitions 6 --edge-file graph-part_edgelist_99.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.99_6_thresh0.5.csv"))
```



30%, 4 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.99.fa --threshold 0.3 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.99_4_nomoving.csv --labels-name label --partitions 4 --edge-file graph-part_edgelist_99.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.99_4_nomoving.csv"))
```

30%, 5 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.99.fa --threshold 0.3 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.99_5_nomoving.csv --labels-name label --partitions 5 --edge-file graph-part_edgelist_99.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.99_5_nomoving.csv"))
```

30%, 6 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.99.fa --threshold 0.3 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.99_6_nomoving.csv --labels-name label --partitions 6 --edge-file graph-part_edgelist_99.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.99_6_nomoving.csv"))
```

40%, 4 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.99.fa --threshold 0.4 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.99_4_thresh0.4_nomoving.csv --labels-name label --partitions 4 --edge-file graph-part_edgelist_99.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.99_4_thresh0.4_nomoving.csv"))
```

40%, 5 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.99.fa --threshold 0.4 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.99_5_thresh0.4_nomoving.csv --labels-name label --partitions 5 --edge-file graph-part_edgelist_99.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.99_5_thresh0.4_nomoving.csv"))
```

40%, 6 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.99.fa --threshold 0.4 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.99_6_thresh0.4_nomoving.csv --labels-name label --partitions 6 --edge-file graph-part_edgelist_99.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.99_6_thresh0.4_nomoving.csv"))
```

50%, 4 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.99.fa --threshold 0.5 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.99_4_thresh0.5_nomoving.csv --labels-name label --partitions 4 --edge-file graph-part_edgelist_99.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.99_4_thresh0.5_nomoving.csv"))
```

50%, 5 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.99.fa --threshold 0.5 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.99_5_thresh0.5_nomoving.csv --labels-name label --partitions 5 --edge-file graph-part_edgelist_99.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.99_5_thresh0.5_nomoving.csv"))
```

50%, 6 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.99.fa --threshold 0.5 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.99_6_thresh0.5_nomoving.csv --labels-name label --partitions 6 --edge-file graph-part_edgelist_99.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.99_6_thresh0.5_nomoving.csv"))
```


## CD-HIT 95%

30%, 4 clusters
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.95.fa --threshold 0.3 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.95_4.csv --labels-name label --partitions 4 --threads 24 --save-checkpoint-path graph-part_edgelist_95.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.95_4.csv"))
```

30%, 5 clusters
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.95.fa --threshold 0.3 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.95_5.csv --labels-name label --partitions 5 --edge-file graph-part_edgelist_95.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.95_5.csv"))
```

30%, 6 clusters
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.95.fa --threshold 0.3 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.95_6.csv --labels-name label --partitions 6 --edge-file graph-part_edgelist_95.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.95_6.csv"))
```

40%, 4 clusters
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.95.fa --threshold 0.4 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.95_4_thresh0.4.csv --labels-name label --partitions 4 --edge-file graph-part_edgelist_95.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.95_4_thresh0.4.csv"))
```

40%, 5 clusters
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.95.fa --threshold 0.4 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.95_5_thresh0.4.csv --labels-name label --partitions 5 --edge-file graph-part_edgelist_95.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.95_5_thresh0.4.csv"))
```

40%, 6 clusters
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.95.fa --threshold 0.4 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.95_6_thresh0.4.csv --labels-name label --partitions 6 --edge-file graph-part_edgelist_95.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.95_6_thresh0.4.csv"))
```

50%, 4 clusters
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.95.fa --threshold 0.5 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.95_4_thresh0.5.csv --labels-name label --partitions 4 --edge-file graph-part_edgelist_95.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.95_4_thresh0.5.csv"))
```

50%, 5 clusters
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.95.fa --threshold 0.5 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.95_5_thresh0.5.csv --labels-name label --partitions 5 --edge-file graph-part_edgelist_95.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.95_5_thresh0.5.csv"))
```

50%, 6 clusters
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.95.fa --threshold 0.5 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.95_6_thresh0.5.csv --labels-name label --partitions 6 --edge-file graph-part_edgelist_95.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.95_6_thresh0.5.csv"))
```



30%, 4 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.95.fa --threshold 0.3 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.95_4_nomoving.csv --labels-name label --partitions 4 --edge-file graph-part_edgelist_95.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.95_4_nomoving.csv"))
```

30%, 5 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.95.fa --threshold 0.3 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.95_5_nomoving.csv --labels-name label --partitions 5 --edge-file graph-part_edgelist_95.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.95_5_nomoving.csv"))
```

30%, 6 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.95.fa --threshold 0.3 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.95_6_nomoving.csv --labels-name label --partitions 6 --edge-file graph-part_edgelist_95.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.95_6_nomoving.csv"))
```

40%, 4 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.95.fa --threshold 0.4 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.95_4_thresh0.4_nomoving.csv --labels-name label --partitions 4 --edge-file graph-part_edgelist_95.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.95_4_thresh0.4_nomoving.csv"))
```

40%, 5 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.95.fa --threshold 0.4 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.95_5_thresh0.4_nomoving.csv --labels-name label --partitions 5 --edge-file graph-part_edgelist_95.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.95_5_thresh0.4_nomoving.csv"))
```

40%, 6 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.95.fa --threshold 0.4 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.95_6_thresh0.4_nomoving.csv --labels-name label --partitions 6 --edge-file graph-part_edgelist_95.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.95_6_thresh0.4_nomoving.csv"))
```

50%, 4 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.95.fa --threshold 0.5 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.95_4_thresh0.5_nomoving.csv --labels-name label --partitions 4 --edge-file graph-part_edgelist_95.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.95_4_thresh0.5_nomoving.csv"))
```

50%, 5 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.95.fa --threshold 0.5 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.95_5_thresh0.5_nomoving.csv --labels-name label --partitions 5 --edge-file graph-part_edgelist_95.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.95_5_thresh0.5_nomoving.csv"))
```

50%, 6 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.95.fa --threshold 0.5 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.95_6_thresh0.5_nomoving.csv --labels-name label --partitions 6 --edge-file graph-part_edgelist_95.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.95_6_thresh0.5_nomoving.csv"))
```


## Simple initialization

30%, 4 clusters, no moving, simple initialization
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.3 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_4_nomoving_simple.csv --no-moving --labels-name label --partitions 4 --threads 24 --initialization-mode simple
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_4_nomoving_simple.csv"))
```

40%, 4 clusters, no moving, simple initialization
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.4 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_4_nomoving_thresh0.4_simple.csv --no-moving --labels-name label --partitions 4 --threads 24 --initialization-mode simple
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_4_nomoving_thresh0.4_simple.csv"))
```

50%, 4 clusters, no moving, simple initialization
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.5 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_4_nomoving_thresh0.5_simple.csv --no-moving --labels-name label --partitions 4 --threads 24 --initialization-mode simple
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_4_nomoving_thresh0.5_simple.csv"))
```


30%, 5 clusters, no moving, simple initialization
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.3 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_5_nomoving_simple.csv --no-moving --labels-name label --partitions 5 --threads 24 --initialization-mode simple
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_5_nomoving_simple.csv"))
```

40%, 5 clusters, no moving, simple initialization
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.4 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_5_nomoving_thresh0.4_simple.csv --no-moving --labels-name label --partitions 5 --threads 24 --initialization-mode simple
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_5_nomoving_thresh0.4_simple.csv"))
```

50%, 5 clusters, no moving, simple initialization
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.5 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_5_nomoving_thresh0.5_simple.csv --no-moving --labels-name label --partitions 5 --threads 24 --initialization-mode simple
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_5_nomoving_thresh0.5_simple.csv"))
```



30%, 4 clusters, moving, simple initialization
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.3 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_4_simple.csv --labels-name label --partitions 4 --threads 24 --initialization-mode simple
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_4_simple.csv"))
```

40%, 4 clusters, moving, simple initialization
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.4 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_4_thresh0.4_simple.csv --labels-name label --partitions 4 --threads 24 --initialization-mode simple
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_4_thresh0.4_simple.csv"))
```

50%, 4 clusters, moving, simple initialization
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.5 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_4_thresh0.5_simple.csv --labels-name label --partitions 4 --threads 24 --initialization-mode simple
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_4_thresh0.5_simple.csv"))
```


30%, 5 clusters, moving, simple initialization
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.3 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_5_simple.csv --labels-name label --partitions 5 --threads 24 --initialization-mode simple
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_5_simple.csv"))
```

40%, 5 clusters, moving, simple initialization
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.4 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_5_thresh0.4_simple.csv --labels-name label --partitions 5 --threads 24 --initialization-mode simple
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_5_thresh0.4_simple.csv"))
```

50%, 5 clusters, moving, simple initialization
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.5 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_5_thresh0.5_simple.csv --labels-name label --partitions 5 --threads 24 --initialization-mode simple
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_5_thresh0.5_simple.csv"))
```


## CD-HIT reduction 90%

30%, 4 clusters
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.90.fa --threshold 0.3 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.90_4.csv --labels-name label --partitions 4 --threads 24 --save-checkpoint-path graph-part_edgelist_90.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.90_4.csv"))
```

30%, 5 clusters
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.90.fa --threshold 0.3 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.90_5.csv --labels-name label --partitions 5 --edge-file graph-part_edgelist_90.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.90_5.csv"))
```

30%, 6 clusters
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.90.fa --threshold 0.3 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.90_6.csv --labels-name label --partitions 6 --edge-file graph-part_edgelist_90.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.90_6.csv"))
```

40%, 4 clusters
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.90.fa --threshold 0.4 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.90_4_thresh0.4.csv --labels-name label --partitions 4 --edge-file graph-part_edgelist_90.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.90_4_thresh0.4.csv"))
```

40%, 5 clusters
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.90.fa --threshold 0.4 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.90_5_thresh0.4.csv --labels-name label --partitions 5 --edge-file graph-part_edgelist_90.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.90_5_thresh0.4.csv"))
```

40%, 6 clusters
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.90.fa --threshold 0.4 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.90_6_thresh0.4.csv --labels-name label --partitions 6 --edge-file graph-part_edgelist_90.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.90_6_thresh0.4.csv"))
```

50%, 4 clusters
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.90.fa --threshold 0.5 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.90_4_thresh0.5.csv --labels-name label --partitions 4 --edge-file graph-part_edgelist_90.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.90_4_thresh0.5.csv"))
```

50%, 5 clusters
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.90.fa --threshold 0.5 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.90_5_thresh0.5.csv --labels-name label --partitions 5 --edge-file graph-part_edgelist_90.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.90_5_thresh0.5.csv"))
```

50%, 6 clusters
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.90.fa --threshold 0.5 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.90_6_thresh0.5.csv --labels-name label --partitions 6 --edge-file graph-part_edgelist_90.csv
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.90_6_thresh0.5.csv"))
```



30%, 4 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.90.fa --threshold 0.3 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.90_4_nomoving.csv --labels-name label --partitions 4 --edge-file graph-part_edgelist_90.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.90_4_nomoving.csv"))
```

30%, 5 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.90.fa --threshold 0.3 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.90_5_nomoving.csv --labels-name label --partitions 5 --edge-file graph-part_edgelist_90.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.90_5_nomoving.csv"))
```

30%, 6 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.90.fa --threshold 0.3 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.90_6_nomoving.csv --labels-name label --partitions 6 --edge-file graph-part_edgelist_90.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.90_6_nomoving.csv"))
```

40%, 4 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.90.fa --threshold 0.4 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.90_4_thresh0.4_nomoving.csv --labels-name label --partitions 4 --edge-file graph-part_edgelist_90.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.90_4_thresh0.4_nomoving.csv"))
```

40%, 5 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.90.fa --threshold 0.4 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.90_5_thresh0.4_nomoving.csv --labels-name label --partitions 5 --edge-file graph-part_edgelist_90.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.90_5_thresh0.4_nomoving.csv"))
```

40%, 6 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.90.fa --threshold 0.4 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.90_6_thresh0.4_nomoving.csv --labels-name label --partitions 6 --edge-file graph-part_edgelist_90.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.90_6_thresh0.4_nomoving.csv"))
```

50%, 4 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.90.fa --threshold 0.5 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.90_4_thresh0.5_nomoving.csv --labels-name label --partitions 4 --edge-file graph-part_edgelist_90.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.90_4_thresh0.5_nomoving.csv"))
```

50%, 5 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.90.fa --threshold 0.5 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.90_5_thresh0.5_nomoving.csv --labels-name label --partitions 5 --edge-file graph-part_edgelist_90.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.90_5_thresh0.5_nomoving.csv"))
```

50%, 6 clusters, no moving
```
graphpart precomputed --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part_cdhit_0.90.fa --threshold 0.5 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_cdhit0.90_6_thresh0.5_nomoving.csv --labels-name label --partitions 6 --edge-file graph-part_edgelist_90.csv --no-moving
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_cdhit0.90_6_thresh0.5_nomoving.csv"))
```



## No moving option

30%, 4 clusters
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.3 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_40_nomoving.csv --no-moving --labels-name label --partitions 4 --threads 24
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_4_nomoving.csv"))
```

40%, 4 clusters
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.4 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_4_nomoving_thresh0.4.csv --no-moving --labels-name label --partitions 4 --threads 24
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_4_nomoving_thresh0.4.csv"))
```

50%, 4 clusters
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.5 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_4_nomoving_thresh0.5.csv --no-moving --labels-name label --partitions 4 --threads 24
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_4_nomoving_thresh0.5.csv"))
```

60%, 4 clusters
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.6 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_4_nomoving_thresh0.6.csv --no-moving --labels-name label --partitions 4 --threads 24
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_4_nomoving_thresh0.6.csv"))
```


40%, 5 clusters
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.4 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_5_nomoving_thresh0.4.csv --no-moving --labels-name label --partitions 5 --threads 24
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_5_nomoving_thresh0.4.csv"))
```

50%, 5 clusters
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.5 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_5_nomoving_thresh0.5.csv --no-moving --labels-name label --partitions 5 --threads 24
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_5_nomoving_thresh0.5.csv"))
```

60%, 5 clusters
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.6 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_5_nomoving_thresh0.6.csv --no-moving --labels-name label --partitions 5 --threads 24
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_5_nomoving_thresh0.6.csv"))
```


30%, 6 clusters
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.3 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_6_nomoving.csv --no-moving --labels-name label --partitions 6 --threads 24
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_6_nomoving.csv"))
```

40%, 6 clusters
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.4 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_6_nomoving_thresh0.4.csv --no-moving --labels-name label --partitions 6 --threads 24
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_6_nomoving_thresh0.4.csv"))
```

50%, 6 clusters
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.5 --out-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Graph-part_results/graphpart_res_6_nomoving_thresh0.5.csv --no-moving --labels-name label --partitions 6 --threads 24
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_6_nomoving_thresh0.5.csv"))
```


## Partitioning within classes

30%, 6 clusters
```{r}
combine_and_plot_graphpart_res(type = "6", datasets)
```

30%, 6 clusters, no moving
```{r}
combine_and_plot_graphpart_res(type = "6_nomoving", datasets)
```

30%, 4 clusters
```{r}
combine_and_plot_graphpart_res(type = "4", datasets)
```

30%, 4 clusters, no moving
```{r}
combine_and_plot_graphpart_res(type = "4_nomoving", datasets)
```

40%, 4 clusters, no moving
```{r}
combine_and_plot_graphpart_res(type = "4_nomoving_thresh0.4", datasets)
```

50%, 4 clusters, no moving
```{r}
combine_and_plot_graphpart_res(type = "4_nomoving_thresh0.5", datasets)
```

40%, 5 clusters, no moving
```{r}
combine_and_plot_graphpart_res(type = "5_nomoving_thresh0.4", datasets)
```

50%, 5 clusters, no moving
```{r}
combine_and_plot_graphpart_res(type = "5_nomoving_thresh0.5", datasets)
```

40%, 6 clusters, no moving
```{r}
combine_and_plot_graphpart_res(type = "6_nomoving_thresh0.4", datasets)
```

50%, 6 clusters, no moving
```{r}
combine_and_plot_graphpart_res(type = "6_nomoving_thresh0.5", datasets)
```



## Threshold = 30%

### Needle, 11 clusters
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.3 --out-file graphpart_res_11.csv --labels-name label --partitions 11 --threads 20
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_11.csv"))
```

### Needle, 6 clusters
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.3 --out-file graphpart_res_6.csv --labels-name label --partitions 6 --threads 20
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_6.csv"))
```

### Needle, 4 clusters
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.3 --out-file graphpart_res_4.csv --labels-name label --partitions 4 --threads 20
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_4.csv"))
```

### mmseqs2, 11 clusters
```
graphpart mmseqs2 --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.3 --out-file graphpart_res_11_mmseqs.csv --labels-name label --partitions 11
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_11_mmseqs.csv"))
```

### mmseqs2, 6 clusters
```
graphpart mmseqs2 --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.3 --out-file graphpart_res_6_mmseqs.csv --labels-name label --partitions 6 
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_6_mmseqs.csv"))
```

### mmseqs2, 4 clusters
```
graphpart mmseqs2 --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.3 --out-file graphpart_res_4_mmseqs.csv --labels-name label --partitions 4 
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_4_mmseqs.csv"))
```


## Threshold = 40%

### Needle, 11 clusters
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.4 --out-file graphpart_res_11_thresh0.4.csv --labels-name label --partitions 11 --threads 20
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_11_thresh0.4.csv"))
```

### Needle, 6 clusters
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.4 --out-file graphpart_res_6_thresh0.4.csv --labels-name label --partitions 6 --threads 20
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_6_thresh0.4.csv"))
```

### Needle, 4 clusters
```
graphpart needle --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.4 --out-file graphpart_res_4_thresh0.4.csv --labels-name label --partitions 4 --threads 20
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_4_thresh0.4.csv"))
```

### mmseqs2, 11 clusters
```
graphpart mmseqs2 --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.4 --out-file graphpart_res_11_mmseqs_thresh0.4.csv --labels-name label --partitions 11
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_11_mmseqs_thresh0.4.csv"))
```

### mmseqs2, 6 clusters
```
graphpart mmseqs2 --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.4 --out-file graphpart_res_6_mmseqs_thresh0.4.csv --labels-name label --partitions 6
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_6_mmseqs_thresh0.4.csv"))
```

### mmseqs2, 4 clusters
```
graphpart mmseqs2 --fasta-file ~/Dropbox/Projekty/BioNgramProjects/PlastoGram/Sequences/Datasets_for_graph-part.fa --threshold 0.4 --out-file graphpart_res_4_mmseqs_thresh0.4.csv --labels-name label --partitions 4
```
```{r}
plot_graphpart_res(paste0(data_path, "Graph-part_results/graphpart_res_4_mmseqs_thresh0.4.csv"))
```
